MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-24 paper.Rmd
Tidying paper.

Input data for the PFU Database can be found in @Marshall:2023aa.
Access to the PFU Database can be obtained by correspondence 
with author [PEB](mailto:P.E.Brockway@leeds.ac.uk)^[Access to the PFU Database
is restricted to those who have access to [IEA WEEB data][link-ieaweeb].].

@@

# Citations

Citations to entries in paper.bib should be in
[rMarkdown](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html)
format.

If you want to cite a software repository URL (e.g. something on GitHub without a preferred
citation) then you can do it with the example BibTeX entry below for @fidgit.

For a quick reference, the following citation commands can be used:
- `@author:2001`  ->  "Author et al. (2001)"
- `[@author:2001]` -> "(Author et al., 2001)"
- `[@author1:2001; @author2:2001]` -> "(Author1 et al., 2001; Author2 et al., 2002)"

@@

We acknowledge contributions from Brigitta Sipocz, Syrtis Major, and Semyeong
Oh, and support from Kathryn Johnston during the genesis of this project.

>>>>

Input data for the PFU Database can be found in @Marshall:2023aa.
Access to the PFU Database can be obtained via correspondence 
with author [PEB](mailto:P.E.Brockway@leeds.ac.uk)^[Access to the PFU Database
is restricted to those who have access to [IEA WEEB data][link-ieaweeb].].

@@

@@

Do we have any acknowledgements?
